PLANETESIMAL ACCRETION AT SHORT ORBITAL PERIODS

### 2021-09-22 main.tex
Summary at end of intro

Outline of paper

Intro text goes here \citep{Wallace2019}

\section{Overview of Planetesimal Accretion}

\section{Methods}

@@

\section{Results}

@@

\section{Simplifying Assumptions}

>>>>

In section \ref{sec:theory} we provide an overview of the theory behind planetesimal accretion and argue that assumptions to derive the well-known modes of growth are only valid at sufficiently long orbital periods. We then motivate the need for N-body simulations to study this problem and describe the code used, along with how our initial conditions were constructed in section \ref{sec:methods}. In section \ref{sec:results}, we present parameter study of planetesimal accretion using a series of simulations of narrow annuli at various orbital periods. We also present a set of simulations starting with a much wider planetesimal disk and demonstrate that a transition between accretion modes occurs at moderately small ($\simeq$ 50d) orbital periods. Next, we assess the impact of simplifications made to our collision model on this result in section \ref{sec:assump}. In section \ref{sec:discuss}, we discuss the implications of this multimodal accretion behavior throughout the disk for planet formation models and conclude.

\section{Overview of Planetesimal Accretion}\label{sec:theory}

\section{Methods}\label{sec:methods}

@@

\section{Results}\label{sec:results}

@@

\section{Simplifying Assumptions}\label{sec:assump}
